---
title: "Overview of Gameday"
author: "Sarah McArthur"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Gameday}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

### Gameday Package

This R package allows users to quickly and easily find out whether or not their favourite NHL team plays today, or any other day they may be interested in. It also allows users to view the final NHL scores of today or any day past. All this without ever needing to open a distracting web browser and all from the comfort of your R console.

### Usage

**gday(team, date)**

First we need to load the `gameday` package once installing it from github.

```{r}
library("gameday")
```

Then we can query whether or not our favourite NHL team played on a certain date, for example by using the `gday(team, date)` function.

```{r}
# did the Winnipeg Jets play on 08 Nov 2014?
gday(team = "jets", date = "2014-11-08")

# do the Canucks play today? (note that the Canucks are the default team for this package)
gday(date = Sys.Date())

# will the Canadiens play tomorrow?
gday(team = "montreal", Sys.Date() + 1)
```

** scores(date)**

We might also want to know the NHL scores from a certain day as well, using the `scores(date)` function.

```{r}
scores("2014-11-08")
```

We might want to know something else about the scores from that day. For instance, we can use the `scores()` function is display all the teams from 18 Nov 2014 that were playing at home and won. We will use syntax from the `dplyr` package to help us figure this out.

```{r}
library(dplyr)

scores <- scores("2014-11-08")
scores %>%
	group_by(home) %>% filter(home_score > away_score) %>%
	select(home)
```

### Conclusions

**Credit Where Due**

This week was very busy for me (away in Saskatoon for work), so I did not have much time or energy to dedicate to this assignment. I found a lot of inspiration for this assignment (ie. ideas about how to get going on the function code and writing a vignette) by looking at other students `gameday` repos, as well as the instructors links. But I found the most inspiration on [Derek Chiu's repo](https://github.com/dchiu911/gameday). Thank you Derek for the unintentional help and for having a great assignment built!


**Final Thoughts**

I found the workflow for building a package to be a bit tricky at first - it was difficult for me to remember to use `document()` and `build_vignette()` to get my documents out there before building and loading the newest version of the package. But after a while and a lot of back and forth, I think I've got the hang of it. I also managed to get by with only one Warning and 2 Notes after checking my package's compatibility with CRAN requirements, which is surprsing not bad! Overall, I wish I had more time this week to explore package building and try writing my own package with function I use frequently in my analyses. But, at the very least, now I know that I can build a package in the future for my own use, which is great to know. One excellent example of this idea is [Dean Attali's `RSalad` package](https://github.com/daattali/rsalad).

